### 2014-10-31 contract-language.tex
Demonstrated classfication for getBalance contract

Observe that the contracts $\scc$, $\ccc$ and $\ecc$ are themselves
totally ordered with respect to the $\le$ relation: $\ecc \le \ccc \le
\scc$.  This concurs with the intuition that any contract satisfiable
under $\ecc$ or $\ccc$ is satisfiable under $\scc$, and any contract
that is satisfiable under $\ecc$ is satisfiable under $\ccc$. However,
we are interested in the \emph{weakest} guarantee (among $\ecc$,
$\ccc$, and $\scc$) required to satisfy the contract. We define the
corresponding consistency level as the \emph{consistency class of the
contract}. The classification scheme is presented formally in
Figure~\ref{sem:classify}.

>>>>

Observe that the contracts $\scc$, $\ccc$ and $\ecc$ are themselves
totally ordered with respect to the $\le$ relation: $\ecc \le \ccc \le
\scc$.  This concurs with the intuition that any contract satisfiable
under $\ecc$ or $\ccc$ is satisfiable under $\scc$, and any contract
that is satisfiable under $\ecc$ is satisfiable under $\ccc$. However,
we are interested in the \emph{weakest} guarantee (among $\ecc$,
$\ccc$, and $\scc$) required to satisfy the contract. We define the
corresponding consistency level as the \emph{consistency class of the
contract}. The classification scheme, presented formally in
Figure~\ref{sem:classify}, defines rules to judge consistency class of
a contact. For example, the scheme classifies \cf{getBalance} contract
($\cv_{gb}$) from Sec.~\ref{sec:motivation} as a {\sf
CausallyConsistent} contract, because the sequent $\Delta \vdash \ccc
\Rightarrow \cv_{gb}$ is valid in first-order logic (therefore,
$\cv_{gb} \le \ccc$), whereas the sequent $\Delta \vdash \ecc
\Rightarrow \cv_{gb}$ is invalid (therefore, $\cv_{gb} \not\le \ecc$).
Due to the confinement of our contract language to a decidable subset
of the logic, validity of such sequents can be decided mechanically
allowing us to automate the classification scheme in \name.

### 2014-10-31 motivation.tex
Demonstrated classfication for getBalance contract

In our running example, it is clear that in order to preserve the integrity
constraint, the \cf{withdraw} operation must be strongly consistent.  That is,
given two \cf{withdraw} operations $a$ and $b$, either $a$ is visible to $b$ or
vice versa. Utilizing the primitive relations described in
Section~\ref{sec:sysmod}, we express this application-level consistency
requirement as a contract or specification over \cf{withdraw}:

@@

\noindent For \cf{getBalance}, we construct the following contract:

>>>>

In our running example, it is clear that in order to preserve the integrity
constraint, the \cf{withdraw} operation must be strongly consistent.  That is,
given two \cf{withdraw} operations $a$ and $b$, either $a$ is visible to $b$ or
vice versa. Utilizing the primitive relations described in
Section~\ref{sec:sysmod}, we express this application-level consistency
requirement as a contract or specification ($\cv_w$) over \cf{withdraw}:

@@

\noindent For \cf{getBalance}, we construct the following contract ($\cv_{gb}$):
